%-------------------------
% Resume in Latex
% Author : 
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Riley Mathews} \\ \vspace{1pt}
    \small 646-300-5733 $|$ \href{mailto:rileymathews13@gmail.com}{\underline{rileymathews13@gmail.com}} $|$ 
    \href{https://linkedin.com/in/riley-mathews-1793251a3/}{\underline{linkedin.com/in/Riley}} $|$
    \href{https://github.com/MatherMan}{\underline{github.com/MatherMan}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Diego State University}{GPA: 3.5/4.0}
      {Bachelor of Science in Computer Science, Bachelor of Science in Finance}{May 2025}
   % \resumeSubSubheading{Bachelor of Science in Finance}{Completed May 2023}
   %   \resumeSubheading{Clubs}{ }{Association for Computing Machinery, Eleetcoders Club}{ }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Internship Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer Intern}{Summer 2019}
      {Tourneau}{New York, NY}
      \resumeItemListStart
        \resumeItem{Automated inventory management system using Google Scripts to streamline identification of aged or damaged inventory, resulting in 18\% decrease in stagnant inventory.}
        \resumeItem{Achieved an 18\% reduction in damaged inventory downtime, with an automated workflow that notified store managers of action items and facilitated service requests via customized Google Forms.}
        \resumeItem{Used HTML and CSS to implement front-end enhancements on a website generating over \$50 million in online sales to drive seamless user experiences and design consistency.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Financial Advising Intern}{Summer 2022}
      {Bank of America}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Achieved a 13\% higher than average return rate by identifying requirements.}
        \resumeItem{Developed data-driven strategies for personalized financial planning, utilizing advanced Excel techniques to analyze client data and provide tailored recommendations.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Course Registration} $|$ \emph{NodeJS, Express, React, PostgreSQL, Drizzle ORM}}{September 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed \textbf{RESTful APIs} using \textbf{Node.js} and Express to facilitate seamless data exchange between the backend and frontend, supporting key endpoints for managing majors, students, faculty, users, courses, and scheduled courses.}
            \resumeItem{Leveraged Drizzle ORM with \textbf{PostgreSQL} to define and manage complex data schemas, including relationships between departments, majors, students, faculty, and course schedules.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Personal Block-chain} $|$ \emph{Java, Object Oriented Design, SHA-256 Hashing}}{May 2024}
          \resumeItemListStart
            \resumeItem{Utilized \textbf{object-oriented programming}, file handling, and error management techniques to create a blockchain prototype.}
            \resumeItem{Implemented \textbf{cryptographic hash functions} for block verification and ensured the integrity of data in a chain structure.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Personal Cookbook Website} $|$ \emph{HTML, CSS, JavaScript, Git}}{Dec. 2023 -- Jan. 2024}
          \resumeItemListStart
            \resumeItem{Developed a website using \textbf{HTML}, \textbf{CSS}, and \textbf{JavaScript} to structure and style recipe content.}
            \resumeItem{Utilized \textbf{Git} version control, ensuring smooth continuous code integration.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Other Work Experience}

    \resumeSubHeadingListStart
        \resumeSubheading{Member Services Lead - \textnormal{\textit{S.A.L.T. President}}}{June 2023 - Present}
        {Associated Students of SDSU}{San Diego, CA}
        \resumeItemListStart
            \resumeItem{Elected President of internal leadership group by peers to oversee staff appreciation, community outreach, and drive community-building efforts within the organization.}
            \resumeItem{Increased culture capital and commitment to organizational values, shown by an 11\% increase in employee engagement, by interviewing, onboarding, and training over 30 new staff}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, Assembly} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, NVim, Vim, Vi, VS Code, Visual Studio, LaTeX} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Drizzle ORM, pg, SHA-256}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
